Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-04 paper/ms.tex
Add caption to midplane figure

\begin{figure*}
\plotone{fig/midplane_fit.pdf}
\caption{Caption.}
\label{fig:midplane}
\end{figure*}

>>>>

\begin{figure*}
\plotone{fig/midplane_fit.pdf}
\caption{The local midplane determined at the fiducial Solar radius
($8.2\,\kpc$) for the three FIRE galaxies m12i, m21f, and m12m ({\em left},
{\em center}, and {\em right} panels). The local midplane is determined at a
position $\phi$ by taking the median height of all stars within $R=0.5\,\kpc$
and $z=1\,\kpc$ (in cylindrical coordinates). The procedure is performed again
using the new height $10$ times to converge on the local midplane height. In
order to allow for the possibility that the fiducial Galactocentric coordinate
system is incorrect, we subtract the best fit $A\sin{(\phi+B)}+C$ curve from
each panel --- this figure is reproduced with the original midplane
determination (i.e. before subtracting the best fit sine curve) in
Appendix~\Gus{x}. We then bootstrap resample $1000$ times on all stars within
a $2\,\kpc$ height of the fiducial midplane to determine error bars (95\uth
and 5\uth percentiles), which we report as dashed lines.}
\label{fig:midplane}
\end{figure*}
